Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2019-04-17 thirdPaper/draft/typeConeAssociahedra.tex
last sentence of introduction modified

\smallskip
\noindent
Some of these questions are explicitly indicated throughout the paper.
To conclude, we observe that the associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan, motivating the question to understand the complete realization space of the cluster complex.

>>>>

\smallskip
\noindent
Some of these questions are explicitly indicated throughout the paper.
To conclude, we observe that the associahedra constructed in~\cite{ArkaniHamedBaiHeYan, BazierMatteDouvilleMousavandThomasYildirim} and the present paper describe all polytopal realizations of the $\b{g}$-vector fan.
This motivates the following question: Is it possible to similarly understand the complete realization space of the cluster complex, including all realizations not having the~$\b{g}$-vector fan as their normal fan?
